\documentclass[aspectratio=169]{beamer}

\title[Short Title]{
    ECE 555 Group Presentation
}
\author{
	% \tiny
	Igor Semyonov
	\and Jordan Carnes
	\and Robert Laverne Griffin
}
\institute{
    George Macon University, Department of Electrical and Computer Engineering
}

\input{preamble.tex}

\begin{document}

\begin{frame}
	\vspace{-1.8cm}
	\titlepage
\end{frame}

\begin{frame}
	\frametitle{Why not Just Use C?}
	\framesubtitle{}

	It should not be used for production.

	See \url{https://veresov.pro/cmustdie/}
\end{frame}

\begin{frame}
	\frametitle{Why Rust?}
	\framesubtitle{Type System}

	insert real/fake cat example from \url{https://www.youtube.com/watch?v=z-0-bbc80JM&t=514s}
\end{frame}

\begin{frame}
	\frametitle{Why Rust?}
	\framesubtitle{Safety}

	Insert image of my IDE showing an error such as attempting to use a value after it is moved out of scope.
\end{frame}

\begin{frame}
	\frametitle{Why Rust?}
	\framesubtitle{Ergonomics while remaining fast}

	Here I may include my rust implementation of project 1 and compare it to my C version in both ergonomics, safety, and speed.
\end{frame}

\begin{frame}
	\frametitle{Why Rust?}
	\framesubtitle{Compiler has Super Powers}

	Since the type system has information about our data, both ownership and lifetime, safe parallel processing is much easier. Chunks are a perfect example of this. The typesystem ensures that each chunk references a seperate portion of memory. This is why paraellizing an iterator over a chunks or chunks\_mut object is trivial.
\end{frame}

\begin{frame}
	\frametitle{Rust and CUDA}
	\framesubtitle{Current options}

	\begin{outline}[itemize]
		\1 Rust GPU
		\1 Rust CUDA
	\end{outline}

	Maybe mention other options for GPU programming in rust, like any rust support for ROCm, HIP, intel gaudi, or other.
\end{frame}

\begin{frame}
	\frametitle{Rust and CUDA}
	\framesubtitle{Description of how the Rust-CUDA crate works}
\end{frame}

\begin{frame}
	\frametitle{Rust and CUDA}
	\framesubtitle{Problems with shared memory access in rust, therefore we need to use unsafe}
\end{frame}

\begin{frame}
	\frametitle{Rust and CUDA}
	\framesubtitle{Focusing on Rust CUDA}

	Currently being rebooted and is in active development.

	Uses nvidia's nvvm tool which is built on LLVM 7.
\end{frame}

\begin{frame}
	\frametitle{What is a compiler?}
	\framesubtitle{}

	Description of problems when going straing from source code to machine code.
\end{frame}

\begin{frame}
	\frametitle{The problem LLVM solves}
	\framesubtitle{}

	Description of LLVM and it's intermediate representation and how this has enabled much easier language development.
\end{frame}

\begin{frame}
	\frametitle{NVVM}
	\framesubtitle{}

	How NVVM works
\end{frame}

\begin{frame}
	\frametitle{Rust CUDA and NVVM}
	\framesubtitle{}

	How NVVM is used in Rust CUDA
\end{frame}

\begin{frame}
	\frametitle{Fractals}
	\framesubtitle{Mandelbrot and Burning Ship}
    $c \in \mathbb{C}$ is in the mandelbrot set if the sequence $\{z_n\}$ converges.

	\begin{equation*}
        z_{n+1} := z_n^2 + c \hspace{1cm} z_0 = 0
	\end{equation*}

    The Burning Ship fractal is defined similarly but the sequence is

	\begin{equation*}
        z_{n+1} := (\abs{\re(z_n)} + \abs{\im(z_n)}i)^2 + c \hspace{1cm} z_0 = 0
	\end{equation*}
\end{frame}

\begin{frame}
	\frametitle{Fractals}
	\framesubtitle{Timing Results for 1 frame on CPU and GPU}

    I will add the single, frame timing results here
\end{frame}

\begin{frame}
	\frametitle{Fractals}
	\framesubtitle{Live Demo}

    I plan to be sharing my screen for the presentation and will switch to a live demo here.
\end{frame}

\begin{frame}
	\frametitle{This is a slide}
	\framesubtitle{With a subtitle}

	\begin{columns}
		\begin{column}{0.6\textwidth}
			This is some text in a column. Could be a figure instead.
		\end{column}
		\begin{column}{0.4\textwidth}
			\begin{outline}[itemize]
				\1
				This is a list
				\1
				It is an itemized one
				\1
				Hence the bullets
			\end{outline}
		\end{column}
	\end{columns}
\end{frame}

% \begin{frame}%[t, allowframebreaks]
%     \frametitle{
%         References
%     }
%     % \nocite{thing-we-want-listed-even-though-it-was-never-cited}
%     % \bibliographystyle{amsalpha}
%     \bibliographystyle{apalike}
%     % If you have more than one page of references, you want to tell beamer
%     % to put the continuation section label from the second slide onwards
%     \setbeamertemplate{frametitle continuation}[from second]
%     % and kill the abominable icon
%     \setbeamertemplate{bibliography item}{\Huge$\rightharpoonup$}
%     % \bibliographystyle{siam}
% \end{frame}
% \bibliographystyle{amsalpha}
% \bibliography{../refs}

\end{document}
